% Management Summary

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Management Summary}
\label{management-summary}

%---------------------------------------------------
\subsection*{Situation}\label{introduction}

Web and mobile mapping is moving towards vector tiles. The osm2vectortiles project provides a viable alternative for all developers and cartographers that want to be independent from 3rd party services and build their own services. To be truly useful and gain greater adoption the project's quality needs to be improved and the process scaled to the entire planet and make it updatable.

%---------------------------------------------------
\newpage
\subsection*{Approach}

The process to improve OSM2VectorTiles has been completly open and the feedback of the community was the cornerstone for improving the project. Based off the experience from the successor study thesis components have been refined and made fit for global usage.

%---------------------------------------------------
\subsection*{Result}

The result of this thesis are downloadable vector tiles for the entire world and extracts for over 200 countries and 400 cities downloadable from the project website. The workflow to create the vector tiles is available for everyone to use and is meant to be adapter for other projects that create vector tiles on a global scale.

Over 200 bugs have been fixed and 23 features have been added, most of them requested and detected by the community. The resut of this thesis is not only a thesis and code but a living OSS project that can be maitained and used in the future with real adopters already using it.


\endgroup

\vfill
